Plant-pollintor networks worldwide are composed by the same specific building

### 2021-10-15 Draft/Draft.Rmd
Conclusions...

From a pollinator perpective, we found that generalist network motifs were consistently over-represented (**Figure 2**). For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links. Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the functional groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs). This large effect of bees on the overall patterns is no surprise, as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017]. Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them. However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions. For instance, the group of self incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e, plant nodes with 3 to 4 links).

The observed functional group probabilities on the different motif positions (**Figure 4**) were insufficient to predict most of the observed network motifs (**Figure 5**). This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations. As suggested by @simmons2020, exploring the proportion of these realized network motifs that is competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007]. In addition, we found that just 30% of the possible 5,3250 motif combinations took place. This concurs well with the general idea that plant-pollinator networks have a high porportion of non-realized interactions [@jordano2003; @bascompte2013] which can be also infered to indirect interactions. @olesen2011 also found a similar porportion of non-realized links in comparison with our findings of non-realized indirect interactions (80% and 70%, respectively). Some of this non-observed interactions are propably caused by under-sampling [@olesen2011; @jordano2016]. However, a large portion of the possible interactions do not take place because of life history constraints [i.e., forbidden links; @olesen2011; @bartomeus2016; @jordano2016]. Thus, similarly to the presence of forbidden links at the network level, we also found the existence of forbidden motifs that represented almost two thirds of the total combinations of indirect interactions.

I NEED A LAST PHRASE HERE

Despite the recent efforts in understanding what are the main drivers of plant-pollinator interactions that ultimately shape competitive and facilitative processes, we lack comprehensive understanding of how these processes affect species direct and ultimately indirect interactions at a macroecological scale.

4th: Link ideas...

Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), taxonomical diversity and trait availability limit our ability to properly represent the diverse range of reproductive strategies in natural systems [@dellinger2020].

Further, delimiting both floral visitors and plants with traits could help revealing more trait-matching processes across groups that are not captured when taxonomic rank is used. Another limitation is that our study just considers binary interactions (presence-absence) and does not account for the interaction strength between plant and pollinator species which is essential to understand pollinator impact upon plant reproduction [REF].

. However, the analysis of quantitative motifs have been just recently develop [@bmotifsimmons2019] and more work is needed to understand their ecological implications in mutualistic networks. Moreover, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015]. This biasis are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator networks.

Final one: 
5) Future direction and conclusions (also short). This opens the door to help predicting novel interactions beyond pairwise interactions. We not only know now how the building blocks are structures, but also that who conform this building blocks is not random.

>>>>

From a pollinator perpective, we found that generalist network motifs were consistently over-represented (**Figure 2**). For instance, when we compare motifs with equal structure but inverted, we found that floral visitors had always over-representation in the positions that implied the highest number of links. Despite this is in good agreement with the current view of the generalist tendency of pollinators [@waser1996; @olesen2002; @ollerton2017], we found that this over-representation of the generalist network motifs was largely driven by the functional group of bees (e.g., positions 42, 46, 16, 4, 14 and 35 in motifs 15, 17, 7, 2, 6 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs) while the rest of the functional groups tended to be under-represented in these generalist motifs and over-represented in motif positions with specialist roles (e.g., positions 11, 21, 28 and 34 in motifs 5, 9, 11 and 13, respectively; see **Figure 3** for positions and **Figure 4** for motifs). This large effect of bees on the overall patterns is no surprise, as bees were the functional group with largest number of interaction records in the whole set of networks as also recorded for other broad scale plant-pollinator network studies [@carvalheiro2014; @ollerton2017]. Unlike floral visitors, plant functional groups showed little differences between their maximum and minimum percentile on the different motif positions in the comparison with simulated networks, and thus similar probability of appearing on them. However, the groups that involved higher levels of outcrossing showed a tendency to be more over-represented and probable on the different motif positions. For instance, the group of self-incompatible perennials with large flowers, one of the groups that is expected to have higher levels of outcrossing rate [@goodwillie2010], showed the highest over-representation of all plant functional groups (**Figure 3**); and the group of tall plants with unisexual flowers, the one that is expected to have the highest dependence of pollinators on reproduction [@rodger2021], was the most probable on the generalist motif for plant positions (i.e., plant nodes with 3 to 4 links; **Figure 4**).

The observed functional group probabilities on the different motif positions were insufficient to predict most of the observed network motifs (**Figure 5**). This implies that not just the representation of network motifs types but also the identity of the elements of their structure is influenced by ecological processes that determine under- and over-representation of the different motif combinations. In addition, we found that just 30% of the possible 53,250 motif combinations took place. Thus, similarly to the presence of forbidden links at the network level [@olesen2011; @jordano2016], we also found the existence of forbidden motifs that represented almost two thirds of the total combinations of indirect interactions. This concurs well with the general idea that plant-pollinator networks have a high porportion of non-realized direct interactions [@jordano2003; @bascompte2013], and as a result, also a high proportion of non-realized combinations of indirect interactions. Some of this non-observed interactions are probably due to under-sampling [@dorado2011; @jordano2016]. However, a large fraction of the possible interactions do not take place because of life history constraints such as species co-occurence, trait matching processes and phenological uncoupling [@olesen2011; @bartomeus2016; @jordano2016]. Despite the advances in the understanding on the ecological processes that influence species pairwise interactions [@bartomeus2016; @peralta2020], we still know little of how these processes determine competitive and facilitative interactions in mutualistic networks. Thus, as suggested by @simmons2020, exploring the proportion of these realized network motifs that is competitive or facilitative is a necessary next step to improve our understanding of the architecture of biodiversity [@bascompte2007].

Despite the obvious usefulness of funtional groups in summarizing species ecological roles (e.g., similar reproductive biology and behaviour of pollinators), delimiting species into functional groups is not often trivial. For instance, taxonomic diversity and trait availability limit our ability to properly represent the wide range of reproductive strategies [@dellinger2020] and different clustering analysis can lead to distinct outcomes (e.g., k-means and hierarchical clustering). Further, here we divided floral visitors on the taxonomic rank level because it represented adequately the pollinator species ecological roles but further groupings with trait data could help revealing greater relevance of trait-matching processes on indirect interactions. Moreover, we analysed network motifs focusing exclusively on presence-absence interactions but as suggested by @simmons2020, further work should account for quantitative measurements of interaction strength. Moreover, despite the wide geographical coverage of our plant-pollinator dataset, there are major gaps for some regions of the world with a clear bias towards Europe, America and islands which have long interested ecologist [@macarthur1963; @warren2015]. These biases are also found in global datasets of networks where the data is highly fragmented across space [@poisot2021] and more efforts are needed to capture global patterns of plant-pollinator networks.

In conclusion, by following the framework of @simmons2020 we have been able to explore competitive and facilitative interactions in plant-pollinator networks worldwide and found that indirect interactions are non-random and are more strongly related to neutral processes than any other ecological process. The association between network motifs and functional groups revealead that the combinations of functional groups is also strongly restricted by ecological processes

these groups rely on their ecological role (e.g., generalization versus specialization) and relies also

Further, the different network motifs are associated with different fucntional groups which translates into different ecological roles of these functional groups at macroecological scale.

with specific network motif positions associated to different species ecological roles. This work set the stage to help predicting novel interactions beyond pairwise interactions, to explore the overall importance

Further, bees were the only generalist functional group in comparison with the rest floral visitor groups that appeared more frequently in specialist network motifs. We also found that the the node position was partly associated to the ecological role of plants but without large differences between groups. Our work has explored for the first time worldwide plant-pollinator patterns of indirect interactions and opens the door for predicting novel interactions beyond pairwise interactions.

Final one: 
5) Future direction and conclusions (also short). This opens the door to help predicting novel interactions beyond pairwise interactions. We not only know now how the building blocks are structured but also that who conform this building blocks is not random.
